---
title: "Writing Functions"
author: "Ashley Tseng"
date: "10/24/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Getting Started
```{r}
x_arg = rnorm(n = 30, mean = 4, sd = 2.3)
x_again = rnorm(n = 30, mean = 6, sd = 0.3)
y = rnorm(n = 30, mean = 5, sd = 2)

(x_arg - mean(x_arg)) / sd(x_arg)
(x_again - mean(x_again)) / sd(x_again)
```
This is what we would normally do (pre-functions): Every time we want to calculate the z-scores of x's that have different mean and sd, we would need to change `x` to `x_again`. We can write a function to make this process more efficient.


## My First Function
```{r}
z_scores = function(x_arg) {
  
  z = (x_arg - mean(x_arg)) / sd(x_arg)
  z
  
}

z_scores(x_arg)
```

### Try Out The Function
```{r, error = TRUE}
z_scores(x_arg = x_again)
z_scores(x_arg = y)

z_scores(x_arg = 3)
z_scores(x_arg = "my name is jeff")
z_scores(x_arg = c(TRUE, TRUE, FALSE, TRUE))
z_scores(x_arg = iris)
```
We have a function with a singular argument x. Any time the function is lookking for x, R will look back at `function(x)` and figure out what the user told it `x` was.

### Making modifications to the function to see when the function breaks
```{r}
z_scores = function(x_arg) {
  
  if (!is.numeric(x_arg)) {
    stop("Argument x should be numeric")
  } else if (length(x_arg) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x_arg) / sd(x_arg)
  
  z
}
```



## Multiple Outputs
```{r, error = TRUE}
mean_and_sd = function(input_x) {
  
  if (!is.numeric(input_x)) {
    stop("Argument x should be numeric")
  } else if (length(input_x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }

tibble(
  mean_x = mean(input_x),
  sd_x = sd(input_x)
)

list(
  mean = mean_x, 
  sd = sd_x,
  z_score = (input_x = mean(input_x))/sd(input_x)
  )
}

mean_and_sd(input_x)
```

### Test out the mean_and_sd function
```{r, error = TRUE}
mean_and_sd(input_x = y)
```



## Multiple Inputs
```{r}
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

sim_data %>%
  ggplot(aes(x=x, y=y)) +
  geom_point() 

ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]
```
beta0_hat extracts the intercept, beta1_hat extracts the slope


### Using a function
```{r}
sim_regression = function(n, beta0 = 2, beta1 = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}

sim_regression(n = 3000, beta0 = 17, beta1 = -3)

sim_regression(n = 14, beta0 = 24)
```
 
 
Note that in R, you don't have to name your arguments (R will just assume that the values are in the order of the order that you entered them in [chronological]). The following are the same:
```{r}
sim_regression(n = 3000, beta0 = 17, beta1 = -3)
sim_regression(3000, 17, -3)
```


## Scraping Amazon
```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

### Can write a function to scrape the reviews off Amazon
```{r}
read_page_reviews <- function(url) {
  
  h = read_html(url)
  
  review_titles = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  review_stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  review_text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)

dynamite_reviews
```


## Loading LOTR Data
```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = words, female:male) %>%
  mutate(race = str_to_lower(race)) %>% 
  select(movie, everything()) 
```


## Functions as arguments
```{r}
x = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {
  summ_func(x)
}

my_summary(x, sd)

my_summary(x, IQR)

my_summary(x, var)
```


## Scoping and names
```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
```

